---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MeasuringLandscapeCivilWar

The goal of MeasuringLandscapeCivilWar is to ...

### Citation

Please cite this compendium as:

> Rex W. Douglass and Kristen Harkness, (`r format(Sys.Date(), "%Y")`). Measuring the Landscape of Civil War: Evaluating
Geographic Coding Decisions with Historic Data from
the Mau Mau Rebellion. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Installation

You can install MeasuringLandscapeCivilWar from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rexdouglass/MeasuringLandscapeCivilWar")
```

### Licenses

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse


