---
title: "10 Predicted Effects"
author: "Rex W. Douglass and Kristen Harkness"
date: "12/9/2017"
output: 
  html_notebook:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: inline
---

Demonstrate what kinds of events tend to systematically get excluded. Here, in terms of whether the event would have received an original military coordinate or not.

```{r , results='hide', message=FALSE, warning=FALSE}
rm(list=ls()); gc()
# !diagnostics off
library(MeasuringLandscapeCivilWar)
devtools::load_all()
dir_figures <- glue(getwd(), "/../paper/figures/")

gc()

knitr::opts_knit$set(progress = TRUE, verbose = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8,  warning=FALSE, message=FALSE, cache=TRUE)
options(width = 160)

p_load(Hmisc)
sentence_case <- function(x) capitalize(tolower(gsub("_"," ",x)))


```


```{r}

#Load Events
events_sf <- readRDS(system.file("extdata", "events_sf.Rdata", package = "MeasuringLandscapeCivilWar")) 

events_sf_text_coord_unique <- ddply(events_sf[,c('location_text',
                                    'name_clean','name_cleaner','document_district_clean','map_coordinate_clean_latitude','map_coordinate_clean_longitude')],
                                     .(location_text), transform,
      map_coordinate_has =sum(!is.na(map_coordinate_clean_latitude))
      )

```


Plot the predicted effects for a single model, Mil. Coords or no Mil. Coords

```{R }


pred_cords <- predict_missingness_dv(is.na(events_sf$map_coordinate_clean_latitude))
rf <- pred_cords$xb_model
train <- pred_cords$x_all_pre_dummy
label <- pred_cords$label
x_all_pre_dummy <- pred_cords$x_all_pre_dummy
x_all <- dummy.data.frame(pred_cords$x_all_pre_dummy)
dtrain <- xgb.DMatrix(data=as.matrix( x_all ), 
                      label = label, missing = NA )
testdata_dummy <- dummy.data.frame(pred_cords$x_all_pre_dummy, drop=F)
dtest <- xgb.DMatrix(data=as.matrix( testdata_dummy ),  missing = NA ) 
dtest <- xgb.DMatrix(data=as.matrix( pred_cords$postdummy ),  missing = NA )

```

Importance scores for each variable, predicting the missingness of exact map coordinates as a function of each event's details.

```{r}
importance_importance <- xgb.importance(feature_names=names(pred_cords$x_all_pre_dummy),
                                        model = rf)
xgb.plot.importance(importance_importance)


```



```{r}

histogram=T
scale=2
a <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="document_date_type",minsize=100,
                  scale=scale,histogram=T)

b <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="document_date_best_year",minsize=100,
                  scale=scale,histogram=T)

c <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="initiator_clean_1_aggmed",minsize=100,
                  scale=scale,histogram=T)



d <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="target_clean_1_aggmed",minsize=100,
                  scale=scale,histogram=T)

e <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="type_clean_aggmed",minsize=100,
                  scale=scale,histogram=T)


f <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="document_unit_type",minsize=100,
                  scale=scale,histogram=T)


g <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing", var="document_district_clean",
                  minsize=100, train=pred_cords$x_all_pre_dummy ,
                  scale=scale,histogram=T)

h <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="event_date_clean_year",minsize=100,
                  scale=scale,histogram=T)

#e <- plot_partial_effects(rf=pred_cords$xb_model,
#                  outcome="mapcoordinate_clean_missing",var="locationtext_ruleclean_suffix",minsize=100)

```


```{r}

p_load(cowplot)
final_histogram <- plot_grid(
  
  a+ggtitle(sentence_case('Document Date Type')),
  b+ggtitle(sentence_case('Document Year')),
  c+ggtitle(sentence_case('Initiator')),
  d+ggtitle(sentence_case('Target')),
  e+ggtitle(sentence_case('Act Type')),
  f+ggtitle(sentence_case('Document Unit')),
  g+ggtitle(sentence_case('Document District')),
  h+ggtitle(sentence_case('Event Year')) + ylab(sentence_case("Probability of Missing Military Coordinates")),
  #i+ggtitle('Reporting Office'),
  ncol = 3, align = "hv" ) #,rel_heights=heights)

ggsave(
  filename = glue(dir_figures, "rf_mapcoordinate_clean_missing.pdf"),
  plot = final_histogram, width = 10, height = 8
)

```

```{r}
print(final_histogram)
```




```{r, eval=F}

scale=2
a <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="document_date_type",minsize=100,
                  scale=scale)

b <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="document_date_best_year",minsize=100,
                  scale=scale)

c <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="initiator_clean_1_aggmed",minsize=100,
                  scale=scale)



d <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="target_clean_1_aggmed",minsize=100,
                  scale=scale)

e <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="type_clean_aggmed",minsize=100,
                  scale=scale)


f <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="document_unit_type",minsize=100,
                  scale=scale)


g <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing", var="document_district_clean",
                  minsize=100, train=pred_cords$x_all_pre_dummy ,
                  scale=scale)

h <- plot_partial_effects(rf=pred_cords$xb_model,
                  outcome="mapcoordinate_clean_missing",var="event_date_clean_year",minsize=100,
                  scale=scale)

#e <- plot_partial_effects(rf=pred_cords$xb_model,
#                  outcome="mapcoordinate_clean_missing",var="locationtext_ruleclean_suffix",minsize=100)




p_load(cowplot)
final <- plot_grid(
  a+ggtitle('Document Date Type'),
  b+ggtitle('Document Year'),
  c+ggtitle('Initiator'),
  d+ggtitle('Target'),
  e+ggtitle('Act Type'),
  f+ggtitle('Document Unit'),
  g+ggtitle('Document District'),
  h+ggtitle('Event Year') + xlab("Prob. of Missing Military Coords."),
  #i+ggtitle('Reporting Office'),
  ncol = 3, align = "hv" ) #,rel_heights=heights)
final

ggsave(
  filename = glue(dir_figures, "rf_mapcoordinate_clean_missing_ridgeplot.pdf"),
  plot = final, width = 10, height = 8
)

```

